\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}


\begin{document}

\title{DevTrack AI: An Evidence-Based Traceability and Reporting System for Student Software Projects}

\titlerunning{DevTrack AI}

\author{Pham Duy Hung\inst{1} \and
Nguyen Thanh Dat\inst{1} \and
Nguyen Le Trung Tin\inst{1} \and
Tran Cong Tu\inst{1} \and
Nguyen Minh Hieu\inst{1}}

\authorrunning{N. M. Hieu et al.}

\institute{FPT University, Da Nang, Vietnam}

\maketitle

\input{sections/abstract}
\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_method}
\input{sections/04_proposed}

\begin{thebibliography}{99}

\bibitem{nlpTraceability}
Guo, J.L.C., Steghöfer, J.P., Vogelsang, A., Cleland-Huang, J.: Natural Language 
Processing for Requirements Traceability. arXiv preprint arXiv:2405.10845 (2024).

\bibitem{ragTraceability}
Hey, T., Fuchß, D., Keim, J., Koziolek, A.: Requirements Traceability Link 
Recovery via Retrieval-Augmented Generation. In: International Working 
Conference on Requirements Engineering: Foundation for Software Quality (REFSQ). 
Lecture Notes in Computer Science. Springer, Cham (2025).

\bibitem{crossLevelTraceability}
Mohammad, B., Sonbol, R., Rebdawi, G.: Cross-level Requirement Traceability: 
A Novel Approach Integrating Bag-of-Words and Word Embedding for Enhanced 
Similarity Functionality. arXiv preprint arXiv:2406.14310 (2024).

\bibitem{traceBert}
Lin, J., Liu, Y., Zeng, Q., Jiang, M., Cleland-Huang, J.: Traceability 
Transformed: Generating More Accurate Links with Pre-Trained BERT Models. 
arXiv preprint arXiv:2102.04411 (2021).

\bibitem{releaseNotes}
Nath, S.S., Roy, B.: Towards Automatically Generating Release Notes using 
Extractive Summarization Technique. arXiv preprint arXiv:2204.05345 (2022).

\bibitem{prDescriptions}
Liu, Z., Xia, X., Treude, C., Lo, D., Li, S.: Automatic Generation of Pull 
Request Descriptions. arXiv preprint arXiv:1909.06987 (2019).

\bibitem{commitMessages}
Cortés-Coy, L.F., Linares-Vásquez, M., Aponte, J., Poshyvanyk, D.: On
Automatically Generating Commit Messages via Summarization of Source Code Changes.
In: Proceedings of the 14th IEEE International Working Conference on Source Code
Analysis and Manipulation (SCAM), pp. 275--284 (2014).

\bibitem{teachingMsr}
Codabux, Z., Fard, F., Verdecchia, R., Palomba, F., Di Nucci, D., Recupito, G.: 
Teaching Mining Software Repositories. arXiv preprint arXiv:2501.01903 (2025).

\bibitem{llmSurvey}
Zhang, Q., Fang, C., Xie, Y., Zhang, Y., Yang, Y., Sun, W., Yu, S., Chen, Z.: 
A Survey on Large Language Models for Software Engineering. arXiv preprint 
arXiv:2312.15223 (2024).

\bibitem{llmContribution}
Ferrao, R.C., de Miranda, F., Soler, D.P.: LLM Contribution Summarization 
in Software Projects. arXiv preprint arXiv:2505.17710 (2505).

\end{thebibliography}

\end{document}
